Many of the systems works as intended as is, but none of the are ideal in terms of user interface and many of them do not allow the creation of custom content.
In addition, we only support LAN play, or in the case of mobile platforms WLAN play.

\subsection{Missions}
Following section \ref{dicsussion:missions} a way to solve the problem of incomprehensible json would be to develop a tool for creating missions.
This would involve descriptions for every variable and a user friendly interface from which to create each mission and map.
Having a tool would partially defeat the original purpose of the JSON format, described in section \ref{sec:modules:missions:customcontent}.
The JSON format was chosen for the property of being human readable, which the tool would be designed to do better.

In addition, extending the mission system to include the partially implemented \textit{MissionObjectives} would be desirable.
These could serve as a dynamic stress factor throughout a mission.
This would mean that the outcome of one wave might effect another.

\subsection{Additional tools}
The game currently features systems that could be extended with support for custom content.
An example of this is the trait system discussed in section \ref{dicsussion:traits}.

Furthermore, allowing the users to customize their characters looks, weapons, texture packs, objectives, and the enemies would be desirable to create a completely custom experience.

Tools with user friendly interfaces would allow anyone to create such content.

\subsection{Network}
It is currently only possible to play the game in a local area network.
Further work would involve making the game playable over the Internet, rather than local network only.

Clientside prediction is also something that could be implemented.
Doing this would significantly improve the smoothness of enemy and character movements for all clients.
It is, however, no trivial task, so refactoring of the current network system may be needed.
Currently, some of the RPC's send more data than is necessary, which is also a minor improvement that could be worked on if the network system is being refactored.
Furthermore, with clientside prediction the update rate of networked entities can also be lowered without losing smoothness.
