Our problem statement states: ''\textit{What is required to create a synchronous multiplayer game for mobile devices, which contains both advanced
gameplay and more complex strategical aspects for a mobile device?}''\\
This can be interprets in many ways therefore a specification of the keywords will be made.
The keywords from this statement are:
\begin{itemize}
\item Synchronous multiplayer
\item Mobile devices
\item Advanced gameplay
\item Complex strategical aspects
\end{itemize}
In order to achieve \textbf{synchronous multiplayer} it should be possible to have one or more devices able to be in the same game, and play together. This includes watching each other do real-time actions in the given game world.\\\\
\textbf{Mobile devices} is a very loosely defined in many different contexts, this report will follow Oxford Dictionary and define a mobile devices as: ''A portable computing device such as a smartphone or tablet computer''\\\\
The game should contains \textbf{Advanced gameplay mechanics}, and according to Oxford Dictionary \textit{gameplay} is defined as \textit{''The features of a computer game, such as its plot and the way it is played, as distinct from the graphics and sound effects.''}.\todoanders{Source from oxford here}
In games such as \textit{Candy Crush} \todoanders{Source on candy crush here} the gameplay consist of destroying candy by swapping candy to align three pieces of specific candy, this is achieved by swiping the finger across the screen.
This is a very simple gameplay given there is no deep plot nor any advanced game way to play it. In comparison games such as \textit{StarCraft II} \todoanders{Source on SC2} which has a lot of controls which gives it a very complex way of playing the game.
More advanced controls schemes such as the ones you find in \textit{StarCraft II} requires many buttons to give the user full control of the game.
This is a problem on mobile devices since the screen is already limited in size compared to laptops and PCs, and placing too many buttons will create to much clutter on the small screen.
To reduce the screen clutter a game genre with simpler control scheme will be necessary.\\
The game should however still have the complex plot to withhold the advanced gameplay. 
In order achieve this the advanced gameplay must be achieved through a deep plot or advanced gameplay features.\\\\
\textbf{Complex Strategical Aspect}: The Oxford dictionaries define \textit{strategy} as \textit{``A plan of action designed to achieve a long-term or overall aim''}.\cite{strategyOx}
Giving the player the ability to make meaningful choices would allow for the player to create strategies to achieve its goal.
These choices should not be right or wrong choices, but choices the player can make give the person can make to give a certain advantage in different situations.
An example of this could be a talent-/skill-tree in a MMORPG, which gives the player a variety of choices in order to achieve their goal whether it is killing a boss in the game or battling other players.
As such, we define the strategic aspect of a video game as a series of meaningful choices which the player/players believe will take the person/persons closer to the goal.