\section{Networking}
Since GAME\todobenjamin{correct this when we have found a name for the game} is a multiplayer game using multiple devices, networking is required. This section will describe the implementation of the networking parts.

\subsection{Architecture}
For building up a network architecture two methods is broadly used in games Peer-to-Peer and Client-server based architecture. 

%http://gafferongames.com/networking-for-game-programmers/what-every-programmer-needs-to-know-about-game-networking/

\subsubsection{Client-Server}
The Client-Server model consist of clients and a server. 

In the traditional client server model, the server is where all the computation happens and is communicated out to the client.
Whereas the clients are essentially \textit{dumb terminals} which is computers that purely redirect the input from the user of the client to the server. 
The server then computes what should happen and then send that information back to the clients, that then updates their games state accordingly.


\subsubsection{Peer-to-Peer}
Peer-to-Peer (\textit{P2P}) network model in games ideally consists of turns. 
Each turn the players gathers the different input from each player who then individually executes all the commands on each machine.
The purpose of this is that, given a deterministic game, the game that are running on each individual computer will be running the exact same code. 
Therefore given the game is deterministic the game state will be exactly the same on each computer. 
%http://www.gamasutra.com/view/feature/131503/1500_archers_on_a_288_network_.php

\subsubsection{Comparison}

\subsection{Unity and networking}

\subsection{Connecting to a server}
The first part of connecting to a server is knowing the ip address of the server.
Finding the ip address of a server is not a trivial.
In order for the clients to find a hosted server, that server has to broadcast its address across the whole network.
This can be done by sending packets to a broadcast address and a specified port.
The address 255.255.255.255 is the \textit{this network} broadcast address, which means its broadcasts are limited to the local network.
The server broadcasts its address, the name of the host, and the current amount of players.

When the client is in the server browser, it listens for broadcasts on the same port, and will then construct a server list from the data received.
Clicking on one of the servers will then connect the client to that server.


\subsection{Clientside prediction}
TODO